### 2021-08-04 chapters/results/1_results_rq1.tex
last feedback

\documentclass[../../main]{subfiles}
\begin{document}
\section{Hierarchical clustering}
\label{ch:results_rq1}
In the this section we present the results of the experiment with hierarchical clustering.
We divide the results in two variants. 
The first variant displays the results of clustering with all characteristics.
The second variant displays the results of clustering without the Levensthein distance.
\newline
For each variant and project we display the weighted mutation score to create box-plots.
There are a total of eleven projects and thus also eleven box-plots per variant.
In a box-plot the box is from the first quartile till the third quartile and a line at the median. 
The dots are measurement points laying outside the fences, which are located at Q1  1.5(Q3  Q1) and Q3+1.5(Q3  Q1). 
The whiskers show the range of points that are outside the box but inside the fences.
\newline
Due to the limitation of resources and time we had to omit four source projects from these results. 
The hardware was not equipped to store the amount of generated mutants for these projects, we did not have enough memory.
Trying to cluster these mutants this resulted in a out of memory error.
\newline
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository\cite{rbasarat-repo}.

\subsection{Clustering with all characteristics}
This section displays the results of our clustering algorithm when executed with data that consists of all characteristics.
The results are be grouped based on the percentage in reduction of mutants executed.
We also display the accuracy of the clusters per reduction.
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository\cite{rbasarat-repo}.

@@

\subsection{Clustering without Levenshtein distance}
This section will display the results of our clustering algorithm when executed without the Levenshtein distance.
The results will be grouped based on the reduced percentage of mutants executed.
We will also display the accuracy of the clusters per reduction amount.
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository\cite{rbasarat-repo}.

>>>>

\documentclass[../../main]{subfiles}
\begin{document}
\section{Hierarchical clustering}
\label{ch:results_rq1}
In the this section we present the results of the experiment with hierarchical clustering.
We divide the results in two variants. 
The first variant displays the results of clustering with all characteristics.
The second variant displays the results of clustering without the Levensthein distance.
\newline
For each variant and project we display the weighted mutation score to create box-plots.
There are a total of eleven projects and thus also eleven box-plots per variant.
In a box-plot the box is from the first quartile till the third quartile and a line at the median. 
The dots are measurement points laying outside the fences, which are located at Q1  1.5(Q3  Q1) and Q3+1.5(Q3  Q1). 
The whiskers show the range of points that are outside the box but inside the fences.
\newline
Due to the limitation of resources and time we had to omit four source projects from these results. 
The hardware was not equipped to store the amount of generated mutants for these projects, we did not have enough memory.
Trying to cluster these mutants this resulted in a out of memory error.
\newline
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository in the folder \textit{experiment_results}\cite{rbasarat-repo}.

\subsection{Clustering with all characteristics}
This section displays the results of our clustering algorithm when executed with data that consists of all characteristics.
The results are be grouped based on the percentage in reduction of mutants executed.
We also display the accuracy of the clusters per reduction.
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository in the folder \textit{experiment_results}\cite{rbasarat-repo}.

@@

\subsection{Clustering without Levenshtein distance}
This section displays the results of our clustering algorithm when executed without the Levenshtein distance.
The results are grouped based on the reduced percentage of mutants executed.
We also display the accuracy of the clusters per reduction amount.
The results displayed are the average of the results of the 30 repetitions of the experiment.
The result of each single repetition can be found in our Github repository in the folder \textit{experiment_results}\cite{rbasarat-repo}.
